Data Exploration

### 2019-02-12 src/data_exploration.Rmd
very minor changes... currently working in BASH

```{r}
janpresabmax <- subset (janpresabmax, select = c(occurrence, originalscientificname, id, cell_id_xyzt, temp_depth, salinity_depth, o2_depth, chl_surface, nao_sample, nao_winter))
head(janpresabmax)
```

@@

```{r}
janpresmax <- subset(janpresabmax, occurrence == "1")
janpresmax <- subset (janpresmax, select = -c(occurrence))
janabmax <- subset(janpresabmax, occurrence == "0")
janabmax <- subset (janabmax, select = -c(occurrence))
```

@@

```{r}
library(dismo)
library(rJava)
jar <- paste(system.file(package="dismo"), "C:/Users/bunny/Documents/GitHub/Chapter_1/packrat/lib/x86_64-w64-mingw32/3.5.1/dismo/java/maxent.jar", sep='')
testmax <- maxent(janpresmax, janabmax)
```

>>>>

```{r}
janpresabmax <- subset (janpresabmax, select = c(occurrence, originalscientificname, id, cell_id_xyzt, temp_depth, salinity_depth, o2_depth, chl_surface, nao_sample, nao_winter))
colnames(janpresabmax)[colnames(janpresabmax)=="cell_id_xyzt"] <- "x"
colnames(janpresabmax)[colnames(janpresabmax)=="id"] <- "y"
janpresabmax$x <- gsub("_", "", janpresabmax$x) #this is needed as maxent thinks these are coordinates
head(janpresabmax)
```

@@

```{r}
janpresmax <- subset(janpresabmax, occurrence == "1")
janpresmax <- subset (janpresmax, select = -c(occurrence))
write.csv(janpresmax, "../output/bio/maxenttestjanpr.csv", row.names = FALSE)
janabmax <- subset(janpresabmax, occurrence == "0")
janabmax <- subset (janabmax, select = -c(occurrence))
write.csv(janabmax, "../output/bio/maxenttestjanab.csv", row.names = FALSE)
```

@@

```{r}
library(dismo)
library(rJava)
jar <- paste(system.file(package="dismo"), "C:/Users/bunny/Documents/GitHub/Chapter_1/packrat/lib/x86_64-w64-mingw32/3.5.1/dismo/java/maxent.jar", sep='')
p
testmax <- maxent(janpresmax, janabmax)
```
